Supplementary methods

### 2021-06-29 text/supplemental_methods.Rmd
Adjust width and update xaxis (Effage -> A) for SM3 Fig. Fix A' not italicized in text.

However, to model the risk of cancer effectively we found that it was necessary
not to use the actual age $\A'$ but instead the "effective age" for that
tissue/class type. Our effective age is calculated as:

@@

```{r sm3, fig.height=3, fig.width=3}
sm3.1 <- ggplot(data.frame(x=0:110),aes(x)) + 
  stat_function(fun=function(x) dgamma(x,30.0,29.0/65),geom="area", fill = alpha("black", 0.5)) +
  theme_classic() + 
  scale_x_continuous(limits = c(30, 110), breaks = c(seq(30,110, by =10))) +
  theme(plot.title = element_text(size = 12, hjust = 0.5),
        panel.grid.major = element_line(size = 0.75),
        panel.grid.minor = element_line()) +
  labs(x= expression(paste("Prior for Effage"["tis"])), y = "Probability Density")

sm3.2 <- ggplot(data.frame(x=0:3),aes(x)) + 
  stat_function(fun=function(x) dgamma(x,50.0,49.0/1.0),geom="area", fill = alpha("black", 0.5)) +
  theme_classic() + 
  scale_x_continuous(limits = c(0.5, 1.6), breaks = c(seq(0.6, 1.5, by = 0.2))) +
  theme(plot.title = element_text(size = 12, hjust = 0.5),
        panel.grid.major = element_line(size = 0.75),
        panel.grid.minor = element_line()) +
  labs(x= expression(paste("Prior for Effage"["cl"])), y = "Probability Density")

>>>>

However, to model the risk of cancer effectively we found that it was necessary
not to use the actual age $A'$ but instead the "effective age" for that
tissue/class type. Our effective age is calculated as:

@@

```{r sm3, fig.height=3, fig.width=6}
sm3.1 <- ggplot(data.frame(x=0:110),aes(x)) + 
  stat_function(fun=function(x) dgamma(x,30.0,29.0/65),geom="area", fill = alpha("black", 0.5)) +
  theme_classic() + 
  scale_x_continuous(limits = c(30, 110), breaks = c(seq(30,110, by =10))) +
  theme(plot.title = element_text(size = 12, hjust = 0.5),
        panel.grid.major = element_line(size = 0.75),
        panel.grid.minor = element_line()) +
  labs(x= expression(paste("Prior for A"["0"])), y = "Probability Density")

sm3.2 <- ggplot(data.frame(x=0:3),aes(x)) + 
  stat_function(fun=function(x) dgamma(x,50.0,49.0/1.0),geom="area", fill = alpha("black", 0.5)) +
  theme_classic() + 
  scale_x_continuous(limits = c(0.5, 1.6), breaks = c(seq(0.6, 1.5, by = 0.2))) +
  theme(plot.title = element_text(size = 12, hjust = 0.5),
        panel.grid.major = element_line(size = 0.75),
        panel.grid.minor = element_line()) +
  labs(x= expression(paste("Prior for A"["cl"])), y = "Probability Density")
